Writing News Captions with Bags of Attention

### 2019-10-21 paper/paper.tex
Add results to paper

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

@@

\begin{table*}[t]
	\caption {Results on the GoodNews dataset}
	\label{tab:results-goodnews}
	\centering
	\begin{tabular}{llllllll}
		\toprule
		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr\\
		\midrule
      Biten \etal \cite{Biten2019GoodNews} & 8.92\% & 3.54\% & 1.60\% & 0.83\% & 12.1\% & 4.34\% & 12.8\% \\
      Transformer & 22.6\% & 13.7\% & 8.90\% & 6.15\% & 21.4\% & 10.3\% & 53.3\% \\
      \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Results on the NYTimes+ test set}
	\label{tab:results-nytimes}
	\centering
	\begin{tabular}{llllllll}
		\toprule
		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr \\
		\midrule
      Transformer & 17.2\% & 10.2\% & 6.55\% & 4.55\% & 19.1\% & 8.41\% & 40.4\% \\
      Transformer (location-aware) & 18.4\% & 11.2\% & 7.35\% & 5.16\% & 20.5\% & 9.21\% & 47.6\% \\
      \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Proper name metrics on the NYTimes+ test set}
	\label{tab:results-names}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
        & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
		\midrule
      Transformer & 26.2\% & 31.5\% & 19.6\% & 29.3\% & 17.2\% & 21.3\%  \\
      Transformer (location-aware) & 30.1\% & 35.4\% & 23.6\% & 32.6\% & 22.1\% & 25.4\%   \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Word statistics on the NYTimes+ test set}
	\label{tab:results-stats}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & Caption length  & Unique words \\
      \midrule
      Ground Truths & 18.4 & 17.1 \\
      Transformer  & 12.8 & 11.5 \\
      Transformer (location-aware) & 12.9 & 11.6  \\
		\bottomrule
	\end{tabular}
\end{table*}

>>>>

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{multirow} % creates cells that span multiple rows in a table
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

@@

\begin{table*}[t]
	\caption {Results on the GoodNews dataset}
	\label{tab:results-goodnews}
	\centering
	\begin{tabular}{llllllll}
		\toprule
		 & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr\\
      \midrule
      Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04\% & 3.65\% & 1.71\% & 0.89\% & 12.2\% & 4.37\% & 13.1\% \\
      Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 8.10\% & 3.33\% & 1.60\% & 0.85\% & 11.9\% & 4.23\% & 12.8\% \\
      Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 8.44\% & 3.42\% & 1.62\% & 0.87\% & 12.2\% & 4.30\% & 13.1\% \\
      Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 8.68\% & 3.47\% & 1.58\% & 0.82\% & 12.1\% & 4.23\% & 12.6\% \\
      Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 7.74\% & 3.15\% & 1.45\% & 0.75\% & 11.9\% & 4.10\% & 12.5\% \\
      Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 8.10\% & 3.26\% & 1.48\% & 0.76\% & 12.2\% & 4.17\% & 12.7\% \\
      \midrule
      LSTM + GloVe & 13.6\% & 6.19\% & 3.13\% & 1.81\% & 13.5\% & 5.26\% & 11.9\% \\
      LSTM + RoBERTa &  &  &  &  &  &  &  \\
      Transformer + GloVe &  &  &  &  &  &  &  \\
      Transformer + RoBERTa & 22.7\% & 13.7\% & 8.93\% & 6.17\% & 21.4\% & 10.3\% & 53.9\% \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
   \caption {Proper name metrics on the GoodNews test set. We can't compute rare name statistics
   since train-test split were created using a random shuffle.}
	\label{tab:results-names}
	\centering
	\begin{tabular}{lll}
		\toprule
        & \multicolumn{2}{c}{All names}  \\
        & Recall  & Precision \\
      \midrule
      Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 12.2\% & 16.5\% \\
      Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 12.0\% & 17.1\% \\
      Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 11.7\% & 17.1\% \\
      Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 17.9\% \\
      Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 11.2\% & 19.0\% \\
      Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 11.0\% & 19.2\% \\
      \midrule
      LSTM + GloVe & 10.1\% & 14.9\%  \\
      LSTM + RoBERTa &  &   \\
      Transformer + GloVe & &  \\
      Transformer + RoBERTa & 29.8\% & 34.4\%  \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Word statistics on the GoodNews test set}
	\label{tab:results-stats}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & Caption length  & Unique words \\
      \midrule
      Ground Truths & 18.1 & 17.0 \\
      Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 8.8 \\
      Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
      Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 & 8.4 \\
      Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 & 8.4 \\
      Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 & 7.9 \\
      Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.3 & 8.5 \\
      \midrule
      LSTM + GloVe & 13.9 & 11.4 \\
      LSTM + RoBERTa &  &  \\
      Transformer + GloVe & &  \\
      Transformer + RoBERTa & 15.7 & 13.8 \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Results on the NYTimes+ test set}
	\label{tab:results-nytimes}
	\centering
	\begin{tabular}{llllllll}
		\toprule
		  & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr \\
		\midrule
      Transformer (first 512 tokens) & 17.6\% & 10.4\% & 6.68\% & 4.65\% & 19.1\% & 8.49\% & 41.1\% \\
      Transformer (location-aware) & 19.0\% & 11.7\% & 7.76\% & 5.48\% & 21.1\% & 9.51\% & 51.4\% \\
      \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Proper name metrics on the NYTimes+ test set}
	\label{tab:results-names}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & \multicolumn{2}{c}{All names} & \multicolumn{2}{c}{Rare names in caption } & \multicolumn{2}{c}{Rare names in article } \\
        & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
		\midrule
      Transformer (first 512 tokens) & 26.4\% & 31.5\% & 19.8\% & 29.5\% & 17.7\% & 20.9\%  \\
      Transformer (location-aware) & 31.5\% & 36.8\% & 25.3\% & 33.2\% & 23.5\% & 25.3\%   \\
		\bottomrule
	\end{tabular}
\end{table*}

\begin{table*}[t]
	\caption {Word statistics on the NYTimes+ test set}
	\label{tab:results-stats}
	\centering
	\begin{tabular}{lllllll}
		\toprule
        & Caption length  & Unique words \\
      \midrule
      Ground Truths & 18.4 & 17.1 \\
      Transformer (first 512 tokens)  & 13.1 & 11.7 \\
      Transformer (location-aware) & 13.0 & 11.7  \\
		\bottomrule
	\end{tabular}
\end{table*}
